---
title: "INDIVIDUAL PROJECT 2"
author: "Rojann Francis del Carmen"
date: "2022-12-15"
output: html_document
---

#Individual Project 2
#del Carmen

#Extract 10000 tweets from Twitter using twitteR package including retweets.
#Subset the retweets and the original tweets into a separate file
#Plot the retweets and the original tweets using bar graph in vertical manner.
#Include legends


install.packages('twitteR')
install.packages("RCurl")
install.packages("rtweet")
install.packages("tinytex")
install.packages("plotly")
install.packages("RColorBrewer")
install.packages("stringr")
install.packages("magrittr")
install.packages("tm")
install.packages("wordcloud")
install.packages("wordcloud2")
install.packages("syuzhet")
install.packages("rdfp")
install.packages(c("devtools", "rjson", "bit64", "httr"))
```{r,ECHO = TRUE}
library("twitteR")
library("RCurl")
library(tinytex)
library(rtweet)
library(ggplot2)
library(RColorBrewer)
library(tm)
library(dplyr)
library(wordcloud)
library(wordcloud2)
library(stringr)
library(syuzhet)
library("rdfp")
library("magrittr")
```

```{r,ECHO = TRUE}

CONSUMER_KEY <- "qvs442wnmCeRWBeMcsl54oVat"
CONSUMER_SECRET <- "16PDlKNLN14uXEAvWyczsDtKa3r7uR6bdjgSoSywAXRse8xTsg"
ACCESS_TOKEN <- "1595396460484648960-103J1iDrS4Sirv8RRsQCZYr5cM7Z8a"
ACCESS_SECRET <-  "ejpl7RVDO6Ew6TAlO3AHqYyECmoWJtMV8EGJUUS5YEKZt"

setup_twitter_oauth(consumer_key = CONSUMER_KEY,
                    consumer_secret = CONSUMER_SECRET,
                    access_token = ACCESS_TOKEN,
                    access_secret = ACCESS_SECRET)
```

```{r,ECHO = TRUE}
trendtweets <- searchTwitter("#FIFA",
                             n = 10000,
                             lang = "en",
                             since = "2022-12-04",
                             until = "2022-12-11",
                             retryOnRateLimit = 120)
```
library("dplyr")
```{r,ECHO = TRUE}
TwttoDF <- twListToDF(trendtweets)
class(TwttoDF)
names(TwttoDF)
#View(TwttoDF)[1:5]
head(TwttoDF$text)[1:5]

save(TwttoDF,file = "FIFATwttoDF.Rdata")
```

```{r,ECHO = TRUE}
load(file = "FIFATwttoDF.Rdata")
```

```{r,ECHO = TRUE}
trendSub <- TwttoDF %>% select(text, screenName, created, isRetweet) %>% 
  filter(isRetweet == FALSE)

trendSub1 <- TwttoDF %>% select(text, screenName, created, isRetweet) %>% 
  filter(isRetweet == TRUE)
```
library(ggplot2)
```{r,ECHO = TRUE}
ggplot(data = trendSub, aes(x = created)) +
  geom_histogram(aes(fill = after_stat(count))) +
  xlab("Date") + ylab("Number of tweets") + 
  scale_fill_gradient(low = "gold", high = "blue")
theme(legend.position = "topleft")
```


```{r,ECHO = TRUE}
ggplot(data = trendSub1, aes(x = created)) +
  geom_histogram(aes(fill = after_stat(count))) +
  xlab("Date") + ylab("Number of tweets") + 
  scale_fill_gradient(low = "gold", high = "blue")
theme(legend.position = "topleft")
```
